\TitlePt

### 2016-03-02 introduction.tex
Layout second paragraph of introduction

>>>>

Deriving density-contrasts and geometries from gravity data is an inverse
problem.

The first stage in developing an inversion method is to establish the
functional mapping between the model parameters and the data, known as forward
modeling.

Solving the forward problem in a stable and accurate way is a prerequisite for
inversion.

Different discretizations of the subsurface require different forward modeling
methods.

For local studies, a flat-Earth approximation and discretization into
right-rectangular prisms is the path often chosen (cite Li and Oldenburg,
Fernando, Cristiano, Barnes, etc).

Cite Nagy some way.

Then talk about spherical Earth and tesseroids. Also mention spherical
harmonics solution.
